Time-resolved optical conductivity and Higgs oscillations\\in two-band dirty superconductors

### 2020-11-08 paper/paper_v1.tex
a

\begin{itemize}
	\item This work: 1) Higgs oscillations in two-band sc. with bands in different limits, 2) Nonequilibrium optical conductivity, 3) Leggett mode in dirty-limit, 4) Prediction for MgB$_2$
\end{itemize}

@@

\subsection{Impurity scattering}
In a clean system momentum conservation yields $\mathbf{J}_{i\mathbf{kk'}} \sim
\delta_{\mathbf{kk'}}$, or $\mathbf{J}_{i\mathbf{kk'}} \sim
\delta_{\mathbf{k,k'}\pm\mathbf{q}}$ if a photon wavevector $\mathbf{q}$ is
considered. In disordered systems translational invariance is broken, so that
transitions between states of different momentum are allowed. Here, we adopt the
approach of Murotani and Shimano [] and model the effects of impurities by
means of the Mattis-Bardeen (MB) substitution []. It relies on approximating the
transition matrix elements $J_{i\mathbf{kk'}}$ as a
Lorentzian in momentum transfer space, explicitly written as
\begin{eqnarray*}
	\langle \left|\mathbf{e} \cdot
	\mathbf{J}_{i\mathbf{kk'}}\right|^2\rangle_{\text{Av}}
	&=& \int \frac{d\Omega_\mathbf{k}}{4\pi} \frac{d\Omega_\mathbf{k}'}{4\pi}
	\left|\mathbf{e} \cdot \mathbf{J}_{i\mathbf{kk'}}\right|^2
	\\
	&\approx& \frac{(e v_{F_i})^2}{3 \pi N_i(0)} 
	\frac{\gamma_i}{\left(\varepsilon_{i|\mathbf{k}|}-\varepsilon_{i|\mathbf{k}'|}\right)^2
	+ \gamma_i^2} \,,
\end{eqnarray*}
with Fermi velocity $v_{F_i}$ density of states of the Fermi level $N_i(0)$ and
impurity scattering rate $\gamma_i$. Note that we are considering an effectively
one-dimensional quantity
where all angular degrees of freedom have been averaged out.
Physically, this means that impurity scattering occurs with equal probability
between all states within a shell around the Fermi sphere.
A derivation of this matrix element
following [Murotani] is reviewed in Appendix X.

@@

We are interested in computing the dynamics of the current
$ \mathbf{j} = -\big\langle \frac{\delta \mathcal{H}}{\delta
\mathbf{A}}\big\rangle =
\mathbf{j}_P + \mathbf{j}_D$, consisting of a paramagnetic and diamagnetic
contribution,
\begin{eqnarray*}
  \mathbf{j}_P 
	&=&
  	\sum_{i\mathbf{kk'}}^{}
	\mathbf{J}_{i\mathbf{kk'}}\,
	\left( 
	  \rho_{i\mathbf{kk'}}^{11}
	  -\rho_{i\mathbf{kk'}}^{22}
	  +1
	\right)
	\\
  \mathbf{j}_D &=& -\sum_{i\mathbf{k}\sigma}^{} \frac{s_i e^2}{2m_i} 
  \mathbf{A} \,
	\left( 
	  \rho_{i\mathbf{kk}}^{11}
	  -\rho_{i\mathbf{kk}}^{22}
	  +1
	\right)
\end{eqnarray*}
and we compute the dynamics of the superconducting order parameter
\begin{eqnarray*}
  \Delta_i = \sum_{j\mathbf{k}}^{}U_{ij} 
  \rho_{j\mathbf{kk}}^{21} \,.
\end{eqnarray*}
To apply the MB substitution we further expand above equation of motions in
orders of $A(t)$. To account for effects of a THG response, we consider terms up to
third order. As detailed in Appendix X, the current only has odd order
components $\mathbf{j} = \mathbf{j}\big|_0 +\mathbf{j}\big|_3 + \dots$ and the
gap only contains even contributions of $A$, $\Delta = \Delta\big|_0 +
\Delta\big|_2 +\dots$.

@@

We are left to compute the equations of motion of the
angle-averaged quantities
\begin{eqnarray*}
  R^{1/3,n}_{\varepsilon_{|\mathbf{k}|}} &=& 
  \int_{}^{}\frac{d\Omega_{\mathbf{k}}}{4\pi}
  \int_{}^{}\frac{d\Omega_{\mathbf{k'}}}{4\pi}
  \mathbf{J}_{i\mathbf{kk'}} \, \rho_{i\mathbf{kk'}}^{nn}\big|_{1/3}
  \\
  r^{nm}_{\varepsilon_{|\mathbf{k}|}} &=& 
  \int_{}^{}\frac{d\Omega_{\mathbf{k}}}{4\pi}
  \rho_{i\mathbf{kk}}^{nm}\big|_{2} \,.
\end{eqnarray*}
We solve them numerically using a [Runge-Kutta] solver on a discretized energy grid
$\varepsilon_{|\mathbf{k}_i|}$ of up to $10^3$ points in the interval $\left[
  -\omega_D, \omega_D
\right]$ (why do we use $\omega_D$???).
A detailed derivation and an explicit presentation of the full equations of
motion is given in Appendix X.

@@

Motivated by the experiment of Matsunaga et al. [] we choose parameters
$\Delta_{\text{eq}}=\SI{1.3}{\milli\electronvolt}$,
$\varepsilon_{F}=\SI{1}{\electronvolt}$, $m=0.78 m_e$, $s=1$ that reflect
measurements and ab-initio calculations on NbN [DFT-reference].
The Debye energy for NbN is order order of 
$\omega_D = \SI{5}{\milli\electronvolt}$, but
for better numerical resolvability we choose $\omega_D =
\SI{2}{\milli\electronvolt}$.

@@

Both the oscillation amplitude and $\Delta_{\infty}$ show a
strong dependence on the impurity scattering rate. For $\gamma\rightarrow 0$
they both vanish while they peak at $\gamma\approx
\Delta^{eq}$, see Fig. \ref{fig:singleband-gap}(f). These results underline the
importance of impurity scattering for the excitation efficiency of collective
Higgs modes already uncovered by Refs. [].
In agreement with the argument from Sec. X this dependence is well approximated by
the functional form $\gamma/(\Delta_{eq}^2+\gamma^2)$.

Next we compute the optical conductivity
\begin{eqnarray*}
\sigma(\omega)=\frac{j(\omega)}{i\omega A(\omega)}
\end{eqnarray*}
and plot its real and
imaginary part in Figs. \ref{fig:cond-lin}(a-b) for various impurity
concentrations.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{figures/fig3.pdf}
	\caption{(A,B) Conductivity spectra for sweeped pump-probe delay $\delta
	t_{\text{p-p}}$ to third order in $A$. (C) False-color plot of
$\sigma' $ which was average-subtracted and normalized to show the oscillations.
A phase shift occurs across the resonance at $2\Delta_{\text{eq}}$ of the quench pulse
frequency. (D) Fourier spectrum of panel (C) showing that frequency of
conductivity oscillation is peaked at $2\Delta_{\text{eq}}$.}
\end{figure}
%\begin{comment}
\section{Multi-band superconductivity}
\label{sec:multiband}

\begin{figure}[ht]
	\centering
	\includegraphics[width=\columnwidth]{figures/m-fig1.pdf}
	\caption{Real part $\sigma'$ (A,C) and imaginary part $\sigma''$ (B,D)
		of optical conductivities to first order in $A$ 
	for various impurity scattering rates at $T=\SI{4}{\kelvin}$ (A,B) and
various temperatures at $\gamma/2\Delta=10$. $\sigma'$ show a characteristic
conductivity gap below $T_C$ and both $\sigma'$, $\sigma''$ diverge in the
static limit.}
\label{fig:singleband-gap}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Higgs oscillations}
\label{sec:higgs_oscillations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
	\item Equation for Current
	\item Equation for optical conductivity
	\item Present and discuss equilibrium optical conductivity in Fig. 1 for the four different limit cases, used in the rest of the paper
\end{itemize}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\columnwidth]{figures/fig-cond-2d-fourcases}
  \caption{Caption}
\end{figure}
\begin{figure*}[ht]
  \centering
  \includegraphics[width=\textwidth]{figures/fig-three-pulses}
  \caption{Caption}
\end{figure*}

\begin{itemize}
	\item Equation for $\delta\Delta(t)$
	\item Show and discuss Higgs oscillations in Fig. 2 of the four cases with a suitable pump pulse (refer to appendix B for details about the pump pulse)
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Nonequilibrium optical conductivity}
\label{sec:noneq_cond}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
	\item Equation for nonequilibrium optical conductivity with two pulses. Maybe here more details (instead of appendix), as this is not covered by the Murotani paper
	\item Show and discuss nonequlibrium conductivity in Fig. 3.
	\item More figures of nonequilibrium conductivity? Suggestions: Imaginary part, maybe appendix. Nice 3d plot. Oscillations along cuts.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Leggett mode} 
\label{sec:leggett_mode}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{itemize}
	\item Definition, equation of Leggett mode
	\item Parameters for Fig.4 where Leggett mode occurs
	\item Discuss Fig. 4
	\item Maybe rethink what exactly to show in Fig. 4
	\item New plot of time-resolved conductivity showing Leggett mode?
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{MgB$_2$}
\label{sec:mgb2}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
	\item Parameters which match MgB$_s$
	\item Show prediction in Fig. 6 of equilibrium conductivity, Higgs oscillations, nonequilibrium conductivity
\end{itemize}

\begin{figure}[H]
    \centering
    %\includegraphics[width=\columnwidth]{figures/mgb2.png}
    \Huge{TODO}
    \caption{\label{fig:mgb2}%
    Result with parameters for MgB$_2$ a) Equilibrium optical conductivity, b) Higgs oscillations, c) pump-probe conductivity and spectra}
\end{figure}%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\end{comment}
\appendix
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Mattis-Bardeen substitution}

@@

\section{Model}
\begin{eqnarray}
  \mathcal{H}_0 = \sum_{i\mathbf{k}\sigma}  
	\varepsilon_{i\mathbf{k}}c_{i\mathbf{k}\sigma}^\dagger
	c_{i\mathbf{k}\sigma} + \sum_{i\mathbf{k}}^{}
	\left( \Delta_i c_{i\mathbf{-k}\uparrow }^\dagger
	c_{i\mathbf{k}\downarrow }^\dagger  \right) \,,
\end{eqnarray}

>>>>

@@

\subsection{Impurity scattering}
\label{sec:MB}
In a clean system momentum conservation yields $\mathbf{J}_{i\mathbf{kk'}} \sim
\delta_{\mathbf{kk'}}$, or $\mathbf{J}_{i\mathbf{kk'}} \sim
\delta_{\mathbf{k,k'}\pm\mathbf{q}}$ if a photon wavevector $\mathbf{q}$ is
considered. In disordered systems translational invariance is broken, so that
transitions between states of different momentum are allowed. Here, we adopt the
approach of Murotani and Shimano [] and model the effects of impurities by
means of the Mattis-Bardeen (MB) substitution []. It relies on approximating the
transition matrix elements $J_{i\mathbf{kk'}}$ as a
Lorentzian in momentum transfer space, explicitly written as
\begin{eqnarray}
	\langle \left|\mathbf{e} \cdot
	\mathbf{J}_{i\mathbf{kk'}}\right|^2\rangle_{\text{Av}}
	&=& \int \frac{d\Omega_\mathbf{k}}{4\pi} \frac{d\Omega_\mathbf{k}'}{4\pi}
	\left|\mathbf{e} \cdot \mathbf{J}_{i\mathbf{kk'}}\right|^2
	\\
	&\approx& \frac{(e v_{F_i})^2}{3 \pi N_i(0)} 
	\frac{\gamma_i}{\left(\varepsilon_{i|\mathbf{k}|}-\varepsilon_{i|\mathbf{k}'|}\right)^2
	+ \gamma_i^2} \,,
	\label{eq:MB}
\end{eqnarray}
with Fermi velocity $v_{F_i}$ density of states of the Fermi level $N_i(0)$ and
impurity scattering rate $\gamma_i$. Note that we are considering an effectively
one-dimensional quantity
where all angular degrees of freedom have been averaged out.
Physically, this means that impurity scattering occurs with equal probability
between all states within a shell around the Fermi sphere.
A derivation of this matrix element
following [Murotani] is reviewed in Appendix \ref{apdx:MB}.

@@

We are interested in computing the dynamics of the current
$ \mathbf{j} = -\big\langle \frac{\delta \mathcal{H}}{\delta
\mathbf{A}}\big\rangle =
\mathbf{j}_P + \mathbf{j}_D$, consisting of a paramagnetic and diamagnetic
contribution,
\begin{eqnarray*}
  \mathbf{j}_P 
	&=&
  	\sum_{i\mathbf{kk'}}^{}
	\mathbf{J}_{i\mathbf{kk'}}\,
	\left( 
	  \rho_{i\mathbf{kk'}}^{11}
	  -\rho_{i\mathbf{kk'}}^{22}
	  +1
	\right)
	\\
  \mathbf{j}_D &=& -\sum_{i\mathbf{k}\sigma}^{} \frac{s_i e^2}{2m_i} 
  \mathbf{A} \,
	\left( 
	  \rho_{i\mathbf{kk}}^{11}
	  -\rho_{i\mathbf{kk}}^{22}
	  +1
	\right)
\end{eqnarray*}
and we compute the dynamics of the superconducting order parameter
\begin{eqnarray*}
  \Delta_i = \sum_{j\mathbf{k}}^{}U_{ij} 
  \rho_{j\mathbf{kk}}^{21} \,.
\end{eqnarray*}
To apply the MB substitution we further expand above equation of motions in
orders of $A(t)$. To account for effects of a THG response, we consider terms up to
third order. As detailed in Appendix \ref{apdx:model}, the current only has odd order
components $\mathbf{j} = \mathbf{j}\big|_0 +\mathbf{j}\big|_3 + \dots$ and the
gap only contains even contributions of $A$, $\Delta = \Delta\big|_0 +
\Delta\big|_2 +\dots$.

@@

We are left to compute the equations of motion of the
angle-averaged quantities
\begin{eqnarray*}
  R^{1/3,n}_{\varepsilon_{|\mathbf{k}|}} &=& 
  \int_{}^{}\frac{d\Omega_{\mathbf{k}}}{4\pi}
  \int_{}^{}\frac{d\Omega_{\mathbf{k'}}}{4\pi}
  \mathbf{J}_{i\mathbf{kk'}} \, \rho_{i\mathbf{kk'}}^{nn}\big|_{1/3}
  \\
  r^{nm}_{\varepsilon_{|\mathbf{k}|}} &=& 
  \int_{}^{}\frac{d\Omega_{\mathbf{k}}}{4\pi}
  \rho_{i\mathbf{kk}}^{nm}\big|_{2} \,.
\end{eqnarray*}
We solve them numerically using a [Runge-Kutta] solver on a discretized energy grid
$\varepsilon_{|\mathbf{k}_i|}$ of up to $10^3$ points in the interval $\left[
  -\omega_D, \omega_D
\right]$ (why do we use $\omega_D$???).
A detailed derivation and an explicit presentation of the full equations of
motion is given in Appendix \ref{apdx:model}.

@@

Motivated by the experiment of Matsunaga et al. [] we choose parameters
$\Delta_{\text{eq}}=\SI{1.3}{\milli\electronvolt}$,
$\varepsilon_{F}=\SI{1}{\electronvolt}$, $m=0.78 m_e$, $s=1$ that reflect
measurements and ab-initio calculations on NbN [DFT-reference].
The Debye energy for NbN is order order of 
$\omega_D = \SI{50}{\milli\electronvolt}$, but
for better numerical resolvability we choose $\omega_D =
\SI{20}{\milli\electronvolt}$.

@@

Both the oscillation amplitude and $\Delta_{\infty}$ show a
strong dependence on the impurity scattering rate peaked at $\gamma\approx
\Delta^{eq}$, see Fig. \ref{fig:singleband-gap}(f). For $\gamma\rightarrow 0$
the Higgs resonance vanishes. [Discussion photon $\mathbf{q}$ and $A^2$ term] These results underline the
importance of impurity scattering for the excitation efficiency of collective
Higgs modes uncovered recently [].
We can understand this result by examining the matrix elements of the current
operator, Eq. (\ref{eq:MB}), following the discussion of Sec. \ref{sec:MB}.
Indeed, the $\gamma$-dependence closely follows
the functional form $\gamma/(\Delta_{eq}^2+\gamma^2)$.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{figures/fig3.pdf}
	\caption{(A,B) Conductivity spectra for sweeped pump-probe delay $\delta
	t_{\text{p-p}}$ to third order in $A$. (C) False-color plot of
$\sigma' $ which was average-subtracted and normalized to show the oscillations.
A phase shift occurs across the resonance at $2\Delta_{\text{eq}}$ of the quench pulse
frequency. (D) Fourier spectrum of panel (C) showing that frequency of
conductivity oscillation is peaked at $2\Delta_{\text{eq}}$.}
\label{fig:cond-pp}
\end{figure}

Next we compute the optical conductivity in linear response
\begin{eqnarray*}
  \sigma_0(\omega)\big=\frac{j(\omega)\big|_1}{i\omega A(\omega)} \,.
\end{eqnarray*}
Real and
imaginary parts $\sigma'(\omega),\sigma''(\omega)$ are plotted 
in Fig. \ref{fig:cond-lin}(a-b) for various impurity
concentrations and in Fig. \ref{fig:cond-lin} for various temperatures.
At low temperatures $\sigma'$ shows a clear conductivity gap below $2\Delta^{eq}$. 
In the clean limit, a pronounced coherence peak is observed around $2\Delta$,
reflecting the additional density of states amassed above the quasiparticle gap. 
The above-gap absorption reaches a maximum at $\gamma \sim 2\Delta$ and broadens
into the characteristic dome shape for which the original analytical MB
expression has been derived []. In the $T\rightarrow 0$ limit, the
conductivty shows a condensate peak $\sigma'(\omega)
= \delta(\omega)$ below the gap which is broadened at
finite temperatures.

Higher orders of the optical conductivity include
contributions of collective modes that smooth out the absorption
edge and add spectral weight inside the conductivity gap.
Here, we calculate the non-linear contribution,
$$\sigma(\omega, \delta t_{pp})=\frac{j(\omega)\big|_1+j(\omega)\big|_3}{i\omega
A(\omega)} \,,$$
in a pump-probe setting. To this end, we pump the system with an intense 
pulse of fluence $A=X$ and after a delay of $\delta t_{pp}$, apply a probe
pulse. Following experimental schemes [], we perform two simulations modelling
both pump and probe, $j_{p-p}$, and a pump only $j_{p}$e. 
We then compute the optical conductivity
from the difference in currents $j=j_{p-p}-j_{p}$. This ensures that resilient
components of the pump do not contribute to the optical conductivity.

Figures \ref{fig:cond-pp}(a-b) show the real and imaginary part of the optical
conductivity $\sigma(\omega,\delta t_{pp}$ as a function of frequency and
  pump-probe delay. It can be seen that the additive third-order contribution
  $j\big|_3$ add spectral weight to the conductivity that slightly fills the
  absorption gap. These contributions show clear oscillations for all
  frequencies $\omega$, as can be seen from Fig. \ref{fig:cond-pp}(c) where
  the dome-shaped envelope has been subtracted. A Fourier transform of these
  oscillations is shown in Fig. \ref{fig:cond-pp}(e) indicating that the
  oscillation frequency matches $2\Delta^{eq}$, the resonance frequency of the
  Higgs mode. Our results show that signatures of the Higgs mode are measureable
  in the pump-probe response of the optical conductivity. All features are
  resolvable by present-day experimental techniques. [Discuss agreement with
  experiment]

%\begin{comment}
\section{Multi-band superconductivity}
\label{sec:multiband}

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{figures/m-fig1.pdf}
	\caption{Real part $\sigma'$ (a,c) and imaginary part $\sigma''$ (b,d)
		of optical conductivities to first order in $A$ 
	for various impurity scattering rates at $T=\SI{4}{\kelvin}$ (A,B) and
various temperatures at $\gamma/2\Delta=10$. $\sigma'$ show a characteristic
conductivity gap below $T_C$ and both $\sigma'$, $\sigma''$ diverges as
$1/\omega$ in the static limit.}
\label{fig:cond-lin2}
\end{figure}
\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{figures/fig-cond-2d-fourcases}
  \caption{Time-resolved optical conductivity for the case were bands are in the
  limit (a) clean-clean, (b) clean-dirty, (c) dirty-clean, (d) dirty-dirty.}
\end{figure}

Motivation by the good agreement of the theory with experimental data, we now
discuss the case of a two-band superconductor. Here, the superconducting state
of MgB$_2$ is likely the most widely studied example and we adopt it as a
reference material. We loosely model the
$\pi$- and $\sigma$-bands believed to be responsible for superconductivity by
choosing material parameters 
$\Delta_{\pi}=\SI{3}{\milli\electronvolt}$,
$\Delta_{\sigma}=\SI{7}{\milli\electronvolt}$, 
$\varepsilon_{F,\pi}=\SI{2.9}{\electronvolt}$,
$\varepsilon_{F,\sigma}=\SI{0.7}{\electronvolt}$, 
$m_\pi=0.85m_e$,
$m_\sigma=1.38 m_e$, 
$\omega_D=\SI{50}{\milli\electronvolt}$,
$s_\pi=1$,
$s_\sigma=-1$.

\subsection{Optical conductivity}

\begin{figure*}[ht]
  \centering
  \includegraphics[width=\textwidth]{figures/fig-three-pulses}
  \caption{Time-resolved optical conductivity for three different pulses.}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Leggett mode and THG} 
\label{sec:leggett_mode}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{itemize}
	\item Definition, equation of Leggett mode
	\item Leggett equation of motion (equation for imaginary part of gap)
	  completely decouples from the remaining system of equations!
	\item In light of this - does Leggett mode really couple with Higgs
	  mode? Here the issue of the Fourier-transform comes up again. Is it
	  possible that the Fourier-transform of the whole time-range is the
	  correct approach. A point is that Leggett mode is peaked in between
	  the two gaps, but all oscillation contirbutions above $2\Delta_1$ are
	  damped very fast (exponential) so that at later times it looks like
	  the energy of the mode is $2\Delta_1$.
	\item TGH experiment. Here, let's decompose the THG signal in
	  quasiparticle, Higgs, Leggett contributions and show the THG in two
	  ways. First, a plot as a function of frequency for the four impurity
	  cases. Second, a plot as a function of temperature for the four cases.
	  The two plots should agree qualitatively, since changing the
	  temperature changes the gap (this is what experimentalists do).
	  Additionally, however, thermal effects contribute which might make
	  things a bit harder to see.
\end{itemize}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\end{comment}
\newpage
\appendix
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Mattis-Bardeen substitution}
\label{apdx:MB}

@@

\section{Model}

\label{apdx:model}
\begin{eqnarray}
  \mathcal{H}_0 = \sum_{i\mathbf{k}\sigma}  
	\varepsilon_{i\mathbf{k}}c_{i\mathbf{k}\sigma}^\dagger
	c_{i\mathbf{k}\sigma} + \sum_{i\mathbf{k}}^{}
	\left( \Delta_i c_{i\mathbf{-k}\uparrow }^\dagger
	c_{i\mathbf{k}\downarrow }^\dagger  \right) \,,
\end{eqnarray}
